---
title: "Baby_faces_data_analysis"
format: pdf
---

```{r}
library(tidyverse)
library(dplyr)
```

```{r}
data <-read.csv("~/Documents/2024spring/summer_surf/ICIS_data_analysis/data/BabyFaces2018_ICIS2024.csv")
```

```{r}
str(data)
data_cleaned<-data|>
  filter(PI1CESDRT >= 0 )|>
  filter(PR1BITSPR >=0)|>
  filter(PR1BITSCR>= 0)
```

# problem behaviors
```{r}
model1 <- lm(PR1BITSPR~PI1CESDRT, data = data_cleaned)
summary(model1)
```

The model’s slope coefficient is 0.16919, and the p-value is 1.67e-15. Since this p-value is smaller than the significance level of 0.05, it indicates that there is significant relationship between parental depression and the problem behaviors in children.

# social competence
```{r}
model3 <- lm(PR1BITSCR~PI1CESDRT, data = data_cleaned)
summary(model3)
```

The model’s slope coefficient is -0.035, and the p-value is 0.000575. Since this p-value is smaller than the significance level of 0.05, it indicates that there is significant relationship between parental depression and the social competence in children.

# language skills

## comprehensive volcabulary

```{r}
model4 <- lm(Comprehension.Vocabular~PI1CESDRT, data = data_cleaned)
summary(model4)
```

The model’s slope coefficient is -0.2151, and the p-value is 0.0522. Since this p-value is greater than the significance level of 0.05, it indicates that there is no significant relationship between parental depression and the comprehensive vocabulary development in children.

## productive volcabulary
```{r}
model5 <- lm(Productive.Vocabulary~PI1CESDRT, data = data_cleaned)
summary(model5)
```

The model’s slope coefficient is -0.2084, and the p-value is 0.0267. Since this p-value is smaller than the significance level of 0.05, it indicates that there is significant relationship between parental depression and the productive vocabulary development in children.
